
%!TEX root = ../dissertation.tex

% Types of Attacks
\section{Review Methodology}
\label{sec:methodology}

The methodology adopted for this review is systematic, structured, and heavily influenced by an extensive study of ``A Review of Security and Privacy Concerns in the Internet of Things (IoT)\cite{aqeel2022review}", which acted as a crucial base for this research. The study was organized into several phases, from identifying the relevant literature on IoT security, to assessing the identified resources, and finally, synthesizing the relevant information.

\subsection{Identification of Sources}
The research process commenced with the identification of a range of sources to ensure comprehensive coverage of the topic. Numerous databases such as IEEE Xplore, ScienceDirect, Google Scholar, and ACM Digital Library were examined to locate recent and pertinent papers. Keywords used included ``IoT," ``IoT Security," ``IoT Threats," ``IoT Vulnerabilities," ``Blockchain and IoT," ``AI and IoT," ``Spoofing," ``Sybil attacks," ``MitM," ``DDoS," ``Buffer overflow," and combinations of these. The references of the initially identified sources, including the foundational paper ``A Review of Security and Privacy Concerns in the Internet of Things (IoT)" and its references, were inspected for additional relevant studies.

\subsection{Screening and Selection}

Post gathering an extensive list of potential sources, each paper's title, abstract, and keywords were examined to gauge their relevance to the topic. To ensure a comprehensive review, the selected papers covered different aspects of IoT security, including a variety of threats, the challenges of IoT security, proposed solutions, and the use of new technologies like blockchain, AI, and machine learning in IoT security.

Through this systematic approach, the review methodology provided a robust foundation for a comprehensive understanding of IoT security, its challenges, and the ongoing efforts to address them. It provided a broad overview, as well as a detailed examination of specific issues and potential solutions, offering a holistic and in-depth look into the security and privacy concerns of IoT.
